NumPy---Array Programming in Python

### 2020-01-16 body.tex
More minor edits

Various libraries build on and extend this functionality to further enrich the
ecosystem of available tools.  For example, SciPy adds various mathematical,
scientific, and engineering routines; Pandas provides indexed arrays, known as
dataframes; xarray implements arrays with labeled axes; and Matplotlib
generates publication-ready figures and visualizations.  Employing these
low-level array-aware functions are several widely used technique-specific libraries,
including scikit-learn (machine learning), scikit-image (image processing),
statsmodels (statistics),  networkx (graphs and complex networks) \cite{SciPyProceedings_11}, and Napari
(volumetric image visualization).

@@

Furthermore, pursuing solutions to these challenges are deemed out of scope for NumPy development. The community's efforts to fill the resultant gaps therefore led to a proliferation of arrays (Fig.~\ref{fig:array-proliferation}): distributed arrays, GPU arrays, delayed execution arrays, sparse arrays, foreign language arrays, and more.

@@

Python is already a good choice for many standard programming tasks such as
cleaning data, interacting with web resources, and parsing text.
It has a wide range of libraries for many different tasks.
Adding fast array operations and linear algebra allows the scientist to do all
their work with within the same language---and one that has the advantage of
being famously easy to learn and teach.

@@

Lastly, NumPy benefited greatly from the simplicity of its underlying data structure, which made it a natural standard for exchanging array data between libraries.  It also made it relatively easy for other
libraries to develop fast and memory-efficient compiled code, usually in C or
Fortran, that could manipulate these arrays and pass them back to Python.

>>>>

Various libraries build on and extend this functionality to further enrich the
ecosystem of available tools.  For example, SciPy adds various mathematical,
scientific, and engineering routines; Pandas provides indexed arrays, known as
dataframes; xarray implements arrays with labeled axes; and Matplotlib
generates publication-ready figures and visualizations.  Employing these
low-level array-aware functions are widely used technique-specific libraries,
including scikit-learn (machine learning), scikit-image (image processing),
statsmodels (statistics),  networkx (graphs and complex networks)
\cite{SciPyProceedings_11}, and Napari (volumetric image visualization).

@@

Furthermore, pursuing solutions to these challenges is out of scope for
NumPy development. The community's efforts to fill the resultant gaps therefore
led to a proliferation of arrays (Fig.~\ref{fig:array-proliferation}):
distributed arrays, GPU arrays, delayed execution arrays, sparse arrays,
foreign language arrays, and more.

@@

Python is already a good choice for standard programming tasks such as
cleaning data, interacting with web resources, and parsing text.
It has a wide range of libraries for different tasks.
Adding fast array operations and linear algebra allows the scientist to do all
their work with within the same language---and one that has the advantage of
being famously easy to learn and teach.

@@

Lastly, NumPy benefited greatly from the simplicity of its underlying data structure, which made it a natural standard for exchanging array data between libraries.  It also made it easy for other
libraries to develop fast and memory-efficient compiled code, usually in C or
Fortran, that could manipulate these arrays and pass them back to Python.

### 2020-01-16 methods.tex
More minor edits

The random number generator library in NumPy provides several alternative
\emph{bit stream generators} that provide the core function of generating
random integers.
A higher-level generator class that implements an assortment of
probability distributions is provided. It includes the beta, gamma
and Weibull distributions, the univariate and multivariate normal
distributions, and more.

@@

Over the course of its history, NumPy has attracted PRs by 823 contributors.
However, its development relies heavily on a relatively small number
of active maintainers, who share more than half of the contributions among
themselves.

>>>>

The random number generator library in NumPy provides alternative
\emph{bit stream generators} that provide the core function of generating
random integers.
A higher-level generator class that implements an assortment of
probability distributions is provided. It includes the beta, gamma
and Weibull distributions, the univariate and multivariate normal
distributions, and more.

@@

Over the course of its history, NumPy has attracted PRs by 823 contributors.
However, its development relies heavily on a small number
of active maintainers, who share more than half of the contributions among
themselves.
